SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-10-05 scipy-1.0/paper.tex
Add references to CiSE 2007 issue

In April 2006, Paul
Dubois\footnote{https://mail.python.org/pipermail/numpy-discussion/2006-April/007487.html} wrote
to the NumPy mailing list:
\begin{quote}
IEEE's magazine, Computing in Science and Engineering (CiSE), has asked me
to put together a theme issue on the use of Python in Science and
Engineering. I will write an overview to be accompanied by 3-5 articles [. . .]
that show a diverse set of applications or
tools, to give our readers a sense of whether or not Python might be useful
in their own work.
\end{quote}
Python had a strong enough presence in science and engineering so that
editors were soliciting a special issue, but it was still niche enough
that the average reader would need additional information in order
to decide whether it would ``be useful in their own work.''
In the resulting CiSE May/June 2007 special issue, Paul's overview\cite{dubois2007guest}
stated:
\begin{quote}
LLNL now has many Python-based efforts built from scratch or wrapped around
legacy codes [. . .] hundreds of thousands
of lines of C++, Python, and Fortran 95, all working together just as we hoped,
doing compute-intensive calculations on massively parallel computers.
\end{quote}
%https://www.computer.org/csdl/mags/cs/2007/03/c3007.html
(steering code)
\cite{oliphant2007python}
\cite{perez2007ipython}
\cite{hunter2007matplotlib}
research applications ...

@@

CiSE 2011 special issue

\cite{vanderwalt2008scipy}
\cite{peterson2009f2py}
\cite{millman2011python}
\cite{perez2011python}
\cite{vanderwalt2011numpy}
\cite{behnel2011cython}
\cite{pedregosa2011scikit}
\cite{vanderwalt2014scikit}
\cite{meurer2017sympy}

>>>>

In April 2006, Paul
Dubois\footnote{https://mail.python.org/pipermail/numpy-discussion/2006-April/007487.html} wrote
to the NumPy mailing list:
\begin{quote}
IEEE's magazine, Computing in Science and Engineering (CiSE), has asked me
to put together a theme issue on the use of Python in Science and
Engineering. I will write an overview to be accompanied by 3-5 articles [. . .]
that show a diverse set of applications or
tools, to give our readers a sense of whether or not Python might be useful
in their own work.
\end{quote}
In the resulting CiSE May/June 2007 special issue, Paul's overview\cite{dubois2007guest}
stated:
\begin{quote}
LLNL now has many Python-based efforts built from scratch or wrapped around
legacy codes [. . .] hundreds of thousands
of lines of C++, Python, and Fortran 95, all working together just as we hoped,
doing compute-intensive calculations on massively parallel computers.
\end{quote}
%https://www.computer.org/csdl/mags/cs/2007/03/c3007.html
(steering code)
SciPy \cite{oliphant2007python}
IPython \cite{perez2007ipython}
Matplotlib \cite{hunter2007matplotlib}
research applications ...

systems biology\cite{myers2007python},
astronomy\cite{greenfield2007reaching},
robotics\cite{krauss2007python},
nanophotonics\cite{bienstman2007python},
partial differential equations\cite{mardal2007using},
neuroimaging\cite{millman2007analysis},
geographic information systems\cite{shi2007python}, and
education\cite{backer2007computational, myers2007pythona},

@@

When Paul edited the CiSE May/June 2007 special issue, Python already had a
strong enough presence in science and engineering so that editors solicited
the special issue, but it was still niche enough that the average reader
would need additional information in order to decide whether it would
``be useful in their own work.''
The follow-up CiSE March/April 2011 Python for Scientists and Engineers
special issue\cite{millman2011python}, focused more on the core parts
of the scientific Python ecosystem\cite{perez2011python} including
NumPy\cite{vanderwalt2011numpy}, Cython\cite{behnel2011cython},
and Mayavi\cite{ramachandran2011mayavi}.

\cite{vanderwalt2008scipy}
\cite{peterson2009f2py}
\cite{pedregosa2011scikit}
\cite{vanderwalt2014scikit}
\cite{meurer2017sympy}
